---
title: "Term paper Radiative Transfer - Ecosystem and Atmosphere Processes"
author: "Simone Massaro - Sugam Subedi"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
documentclass: book
bibliography:
biblio-style: apalike
link-citations: yes
---
# Preface {-}

```{r "setup", include=FALSE}
knitr::opts_knit$set(root.dir = "../../") #set to repo root to correctly load all package
knitr::opts_knit$set(fig.width=16,  fig.height = 9)
knitr::opts_knit$set(dpi=30)
```

```{r, dpi=30}
plot(c(0,0), c(1,1), main="low res")
```
This is the Term Paper for the Ecosystem and Atmosphere Processes course (Winter semester 2020) at Uni Göttingen, prof. Alexander Knohl.

This is a result of a group work between Simone Massaro and Sugam Subedi.

It is part of a course project to develop  a canopy model ..

This term paper is also available in html format at ... which is the suggested way to read it.

#### Task division {-}

The tasks have been divided inside the group:

- *Simone Massaro*: all code development, Model results and Discussion sections.
- *Sugam Subedi*: Theory and Model development sections.