---
title: "Plots for radiative transfer plot"
author: "Simone Massaro"
date: "01/02/21"
output: html_notebook
---

```{r, message = F}
source('../term paper/radiation_utils_test_data.R')
library(scales)
```

```{r}
out <- rad_transf_new_p()

out_plot <- tibble(datetime = input$datetime, night = input$night, mod_sw_out = out$i_up, obs_sw_out = fluxes$sw_out, mod_lw_out = out$l_up, obs_lw_out = fluxes$lw_out)

all_out <- cbind(input, select(fluxes,-time, -Date.Time), out)

days_out <- filter(all_out, datetime > as_date("2018-07-1") & datetime < as_date("2018-07-8"))
```

```{r, include = F}
#' Adds a white and black background when is night
night_bg <- function(){
  list(
    geom_tile(aes(x= datetime, width = dt, y = (max(radiation) + min(radiation))/2, height = max(radiation) - min(radiation) +50, fill = night), alpha = .1, linetype = 0),
  scale_fill_manual(name = NULL, values = c("#ececec", "#555555"), labels = c("day", "night"),
                    guide = guide_legend(override.aes = list(colour = c("#ececec", "#b9b9b9"), alpha = .4))),
    scale_y_continuous(expand = c(0,0))
  )
}

legend_labels <- function(labels, name="", max_width = 10){
  list(
  scale_color_hue(labels = str_wrap(labels, max_width), str_wrap(name, max_width)),
  theme(legend.key.height = unit(40, "pt"))
  )
}
```

Introduction
============

Model output
============

As a first thing we explore the model outputs over a few days.

### Shortwave

we are plotting the four main variables ...

we can see that....

```{r}
days_out %>%
        gather(key = "type", value = "radiation", sw_in, ic, i_up, ig, factor_key = T) %>%
        ggplot() +
        night_bg() +
        geom_line(aes(x = datetime, y = radiation, color = type)) +
        legend_labels(c("Incoming sw", "Absorbed sw canopy", "Upward sw", "Absorbed sw soil")) +
        labs(title = "Time series shortwave variables", subtitle = "modelled output variables (1-8 Jul)", y = "Shortwave radiation (W m-2)")
```

```{r}
days_out %>%
  gather(key = "type", value = "radiation", sw_in, ic, i_up, ig, factor_key = T) %>%
  ggplot() +
  geom_line(aes(x = datetime, y = radiation, color = type)) +
  night_bg() +
  legend_labels(c("Incoming sw",  "Absorbed sw canopy", "Upward sw", "Absorbed sw soil")) +
  labs(title= "Time series shortwave variables", subtitle = "modeled output variables (1-8 Jul)", y = "Shortwave radiation (W m-2)")
```

Shortwave
=========

```{r}
days_out %>%
  gather(key = "type", value = "radiation", lw_in, l_up, lc, lg, factor_key = T) %>%
  ggplot() +
  geom_line(aes(x = datetime, y = radiation, color = type)) +
        night_bg() +
  labs(title= "Time series longwave variables", subtitle = "modelled output variables", y = "Longwave radiation (w m-2)") +
  legend_labels(c("Incoming lw", "Upward lw", "Absorbed lw canopy", "Absorbed lw soil"))

```

LAI over the year
-----------------

```{r}
days <- seq.Date(as.Date("2020-01-01"), as.Date("2020-12-31"), by=1)
LAI <- pmax(Vectorize(get_day_LAI, "datetime")
            (days, pars$max_LAI, pars$leaf_out, pars$leaf_full, pars$leaf_fall, pars$leaf_fall_complete), pars$min_radiation_PAI)

ggplot() + geom_line(aes(x=days, y=LAI)) + ylim(c(0,pars$max_LAI)) + labs(title="LAI over the year") #+theme_bw()
```

Test with sample
================

In this section we create some sample in put and we change only one variable to see how the model output respond to this

Absorbed radiation vs LAI
-------------------------

The increase in LAI increase the amount of radiation absorbed, but then it reaches a peak at even if the LAI increase no more light is absorbed.

```{r}
fake_input_2 <- tibble(
    datetime = as.Date("2020-07-15 12:00"),sw_in = 1000, sw_dif = 100, lw_in = 0, t_soil = 0, t_leaf = 0, zenith = 30,
    LAI = 1:12
)

out_2 <- cbind(rad_transf(input = fake_input_2), sw_in = fake_input_2$sw_in)
labels <-  str_wrap(c("Total incoming sw", "Total absorbed sw", "Absorbed sw sunlit canopy", "Absorbed sw shaded canopy"), 10)

out_2 %>%
        gather("type", "radiation", sw_in, ic, ic_sun, ic_sha, factor_key = T) %>%
        ggplot() +
        geom_line(aes(x=LAI, y=radiation, color=type, linetype=type)) +

        labs(title= "Absorbed shortwave with increasing LAI", subtitle = "Incoming radiation 900 direct + 100 diffuse. Zenith 30°",
             x="LAI (m2 m-2)", y="Absorbed shortwave radiation (W m-2)", color= "", linetype="") +
        scale_color_manual(values = c("black", hue_pal()(3)),labels = labels) +
        scale_linetype_manual(values = c(2,1,4,4), labels = labels) +
        theme(legend.key.height = unit(40, "pt"))

```

Variation of absorbed radiation by the soil and canopy with the variation of LAI

We can see that the overall canopy albedo is constant while the division between soil and canopy changes

```{r}
out_2 %>%
        gather("Radiation_type", "Radiation", c("ic", "ig", "i_up")) %>%
        ggplot() +
        geom_line(aes(x=LAI, y=Radiation, color=Radiation_type, linetype=Radiation_type))
```

Emitted and Absorbed longwave radiation at different temperature
--------------------------------------------------------------

Soil and leaves temperature changes together between 260 and 310 K

TODO: this need to be more interesting! and now is also wrong!

```{r}
fake_input_3 <- tibble(
    datetime = as.Date("2020-07-15 12:00"), # Summer day
    sw_in = 800,
    sw_dif = 100,
    lw_in = 200,
    t_soil = 260:310,
    t_leaf = 260:310,
    zenith = 30,
)
out_3 <- rad_transf(fake_input_3)

out_3 %>% select(-zenith) %>%
        cbind(fake_input_3) %>%
        gather("type", "radiation", c("lc", "l_up")) %>%
        ggplot() +
        geom_line(aes(x=t_leaf, y=radiation, color=type))
```

Absorbed radiation vs zenith
----------------------------

Variation of the fraction of soil radiation that is absorbed with the change of the solar zenith (angle between vertical and sun)

```{r}
fake_input_4 <- tibble(
    datetime = as.POSIXct("2016-07-21 00:00"), # Summer day
    zenith= seq(0,90,5),
    sw_sky_b = 800,
    sw_sky_d = 100,
    lw_sky = 200,
    t_soil = 300,
    t_leaf = 300,
)
out_4 <- radiative_transfer_over_input(fake_input_4, p)

out_4 %>%
        select(-zenith) %>%
        cbind(fake_input_4) %>%
        mutate(absorbed_fraction = ic / (sw_sky_b + sw_sky_d)) %>%
        ggplot() +
        geom_line(aes(x=zenith, y=absorbed_fraction, color="red"))
```

Real data
=========

```{r}
days_out %>%
        gather(key = "type", value = "radiation", i_up, sw_out, factor_key = T) %>%
        ggplot() +
        geom_line(aes(x = datetime, y = radiation, color = type)) +
        night_bg() +
        labs(y = "Outgoing shortwave radiation (w m-2)") +
        legend_labels(labels = c("Modelled", "Observed"), "Outgoing shortwave radiation")
```

scatter plot

```{r}
ggplot(out_plot) +
  geom_abline(aes(intercept = 0, slope = 1, color = "Theory"), key_glyph = "path") +
  geom_point(aes(x = mod_sw_out, y = obs_sw_out)) +
  geom_smooth(aes(x = mod_sw_out, y = obs_sw_out, color = "Regression"), formula = y ~ x, method = 'lm', se = F) +
  labs(title = "Time series shortwave variables", subtitle = "modelled output variables",
        x = "Modelled emitted sw (W m-2)", y = "Observed emitted sw (W m-2)", colour = "Legend")
```

time series

```{r}
days_out %>%
        gather(key = "type", value = "radiation", i_up, sw_out, factor_key = T) %>%
        ggplot() +
        geom_line(aes(x = datetime, y = radiation, color = type)) +
        labs(y = "Outgoing shortwave radiation (w m-2)") +
        night_bg() +
        legend_labels(c("Modelled", "Observed"), "Outgoing shortwave radiation")

```

### Longwave

scatter plot

```{r}
ggplot(data = out_plot) +
        geom_abline(aes(intercept = 0, slope = 1, color="theory"), linetype="dotted") +
        geom_point(aes(x=mod_lw_out, y=obs_lw_out)) +
        geom_smooth(aes(x=mod_lw_out, y=obs_lw_out, color="Regression"), method='lm', formula=y~x, se =F) +
        labs(x="Modelled emitted lw (W m-2)", y="Observed emitted lw (W m-2)")
```

```{r}
night_bg <- function(){
  list(geom_tile(aes(x= datetime, width = dt, y = (max(radiation) + min(radiation))/2, height = max(radiation) - min(radiation) +10, fill = night), alpha = .05, linetype = 0),
  scale_fill_manual(values = c("white", "black"), labels = c("day", "night")),
  theme_bw())
}
```

```{r}
days_out %>%
  gather(key = "type", value="radiation", l_up, lw_out, factor_key = T) %>%
  ggplot() +
  geom_line(aes(x = datetime, y = radiation, color = type)) +
  labs(title= "title", subtitle= "subtitle",
       y = "Outgoing longwave radiation (w m-2)", fill = "", colour=str_wrap("Outgoing longwave radiation", 10)) +
  scale_color_hue(labels = c("Modelled", "Observed")) +
  night_bg()

```

time series

```{r}
days_out %>%
  gather(key = "type", value="radiation", l_up, lw_out, factor_key = T) %>%
  ggplot() +
  geom_line(aes(x = datetime, y = radiation, color = type)) +
  # adding labels and custom background
  geom_tile(aes(x = datetime, width = 3600, y = (max(radiation) + min(radiation))/2, height = max(radiation) - min(radiation) +10, fill = night), alpha = .05, linetype = 0) +
  labs(title= "title", subtitle= "subtitle",
       y = "Outgoing longwave radiation (w m-2)", fill = "", colour=str_wrap("Outgoing longwave radiation", 10)) +
  scale_color_hue(labels = c("Modelled", "Observed")) +
  scale_fill_manual(values = c("white", "black"), labels = c("day", "night")) +
  theme_bw()
```

### Extra

LAI sunlit

```{r}
time_out %>%
  ggplot() +
  geom_line(aes(x = datetime, y = LAI_sunlit)) +
  geom_hline(yintercept = 5, linetype = "dotted")
  labs(y = "LAI sunlit (m2 m-2)")
```

```{r}

```
